Re-visiting the Political Deepfake Videos Misinformation the Public But No More than Other Fake Media (2021)

### 2021-03-24 outputs/paper/Paper3_Output.Rmd
add R libraries bib

---
title: "Re-visiting the Political Deepfake Videos Misinformation the Public But No More than Other Fake Media (2021)"
author: "Yilin Zhu, Jialin Zhao, Renjing Liu"
date: "23/03/2021"
abstract: ""
output: 
  bookdown::pdf_document2:
    latex_engine: xelatex
    toc: FALSE
header-includers:
-  \usepackage{caption}
-  \usepackage{multirow}
bibliography: references.bib
---

@@

# Results
```{r, echo = FALSE, warning=FALSE,regfloat=TRUE}
load(here::here("inputs/deepfake.RData"))
colorscheme <- scale_fill_manual(values=c("#C77CFF","#00BFC4","#7CAE00","#F8766D"))

### diff-in-means
panel1 <- dat %>% filter(treat != "ad", treat != "control") %>%
    mutate(treat = fct_relevel(treat, "skit","audio","text","video")) %>%
    group_by(treat) %>% summarise(estimate=mean(believed_true, na.rm=T), std.error=sd(believed_true, na.rm=T)/sqrt(n())) %>%
    mutate(panel="All\n") %>%
    ggplot(aes(x=treat, y=estimate, ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error)) +
    geom_segment(x=0, xend=4.5, 
                 y=mean(dat$believed_true[!(dat$treat %in% c("ad","control","skit"))], na.rm=T),
                 yend=mean(dat$believed_true[!(dat$treat %in% c("ad","control","skit"))], na.rm=T), 
               size=2, lty=1, color="red", inherit.aes = F) +
    geom_pointrange(aes(shape=treat, fill=treat), position=position_dodge(width=.9), color="black", size=1, stroke=.5) +
    geom_text(aes(group=treat, label=treat, y=estimate+1.96*std.error+0.2), position=position_dodge(width=.9), size=4) +
    scale_shape_manual(values=c(21,22,23,24)) +
    facet_grid(panel ~ .) + 
    scale_x_discrete(expand=c(0.2,0.2)) + colorscheme +
    ylab("") + xlab("") + theme_linedraw() + coord_flip(ylim=c(1,5)) +
    theme(title = element_text(size=5),
          legend.position = "none",
          axis.title.y = element_text(size=16),
          axis.ticks.y = element_blank(),
          axis.text.y = element_blank(),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          strip.text = element_text(size=16),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.x = element_text(size=14, hjust=0))

dd <- bind_rows(
    dat %>% filter(!is.na(agegroup)) %>% filter(treat != "ad", treat !="control") %>%
        mutate(agegroup = as.factor(agegroup)) %>%
        mutate(treat = as.character(treat)) %>%
        mutate(treat = fct_relevel(treat, "skit","audio","text","video")) %>%
        group_by(agegroup,treat) %>%
        summarise(estimate=mean(believed_true, na.rm=T), std.error=sd(believed_true, na.rm=T)/sqrt(n())) %>%
        rename(group=agegroup) %>% mutate(type="By Age\nGroup"))

dd$group <- as_factor(dd$group)

panel3 <- dd %>%
    ggplot(aes(x=group, y=estimate, ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error)) +
    # geom_bar(aes(fill=treat), position=position_dodge(width=.9), color="black", stat="identity") +
    # geom_errorbar(aes(group=treat), position=position_dodge(width=.9), width=.2, size=1) +
    scale_shape_manual(values=c(21,22,23,24)) +
    geom_segment(data = dd %>% 
                     filter(treat != "skit") %>% 
                     group_by(type, treat) %>% mutate(group_x=1:n()) %>% ungroup() %>%
                     group_by(type,group,group_x) %>% 
                     summarise(yint=mean(estimate)),
               aes(x=group_x-.5, xend=group_x+.5, y=yint, yend=yint), 
               size=2, lty=1, color="red", inherit.aes = F) +
    geom_vline(aes(xintercept=1.5), lty=2, color="grey", alpha=0.8) +
    geom_vline(aes(xintercept=2.5), lty=2, color="grey", alpha=0.8) +
    geom_vline(aes(xintercept=3.5), lty=2, color="grey", alpha=0.8) +
    geom_vline(aes(xintercept=4.5), lty=2, color="grey", alpha=0.8) +
    geom_pointrange(aes(shape=treat, fill=treat), position=position_dodge(width=.9), color="black", size=1, stroke=.5) +
    geom_text(aes(group=treat, label=treat, y=estimate+1.96*std.error+0.2), position=position_dodge(width=.9), size=4) +
    facet_grid(type ~ ., space="free", scales="free") +
    scale_x_discrete(expand=c(0.2,0.2)) + colorscheme +
    ylab("mean level of deception in group (95% CI)") + xlab("") + coord_flip(ylim=c(1,5)) + theme_linedraw() +
    theme(title = element_text(size=5),
          legend.position = "none",
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          strip.text = element_text(size=15),
          axis.text.y = element_text(size=14),
          axis.ticks.y = element_blank(),
          axis.text.x = element_text(size=12),
          axis.title.x = element_text(size=18))

pp <- cowplot::plot_grid(panel1, panel3, nrow = 8,
                         align="v",rel_heights = c(0.3, 1))

cowplot::save_plot("figures/topline_exp1_a.pdf", plot = pp, base_height=25.5, base_width=8)
```

```{r fig01, fig.cap="Marginal Means in Exposure Experiment Deception Outcomes",echo = FALSE, warning=FALSE,regfloat=TRUE}
knitr::include_graphics(path = ("figures/topline_exp1_a.pdf"))
```

@@

```{r fig02, fig.cap="Marginal Means in Exposure Experiment Affect Outcomes",echo = FALSE, warning=FALSE,regfloat=TRUE}

knitr::include_graphics(path = "figures/topline_exp1_b_2.pdf")
```

@@

##Detection experiment results
```{r fig03, fig.cap='Marginal Means in Detection Experiment Outcomes',echo = FALSE, warning=FALSE,regfloat=TRUE}
knitr::include_graphics(path = "figures/topline_exp2.pdf")
```

>>>>

---
title: "Re-visiting the Political Deepfake Videos Misinformation the Public But No More than Other Fake Media (2021)"
author: "Yilin Zhu, Jialin Zhao, Renjing Liu"
date: "23/03/2021"
abstract: ""
output: 
  bookdown::pdf_document2:
    latex_engine: xelatex
    toc: TRUE
header-includers:
-  \usepackage{caption}
-  \usepackage{multirow}
bibliography: references.bib
thanks: 'Code and Data are available at: https://github.com/PopeyesIsTheBest/PoliticalDeepFakeVideos.git'
---

@@

# Results

```{r fig01, fig.cap="Marginal Means in Exposure Experiment Deception Outcomes", echo = FALSE, warning=FALSE, fig.align = "center", out.width="80%",fig.width=10, fig.height=40, regfloat=TRUE}
knitr::include_graphics(here::here("figures/topline_exp1_a.pdf"))
```

@@

```{r fig02, fig.cap="Marginal Means in Exposure Experiment Affect Outcomes",echo = FALSE, warning=FALSE, fig.align = "center", out.width="80%",fig.width=10, fig.height=40, regfloat=TRUE}

#knitr::include_graphics(here::here("figures/topline_exp1_b_2.pdf"))
```

@@

##Detection experiment results
```{r fig03, fig.cap='Marginal Means in Detection Experiment Outcomes',echo = FALSE, warning=FALSE, fig.align = "center", regfloat=TRUE}
knitr::include_graphics(here::here("figures/topline_exp2.pdf"))
```
